Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

>>>>

Let us represent the result of the H-V $k$-SJ problem as $\J_k(R_1, ..., R_{k-2},$ $H, V)$. Recall that $\J_k(R_1, ..., R_{k-2},$ $H, V)$ contains all such $k$-tuples $(r_1, ..., r_{k-2}, h, v) \in R_1 \times ... \times R_{k-2} \times H \times V$ satisfying the condition that $h \cap v \bigcap_{i=1}^{k-2} r_i$ is not empty. The condition is equivalent to saying that the intersection point of $h$ and $v$ falls in every $r_i$ of $i \in [k-2]$.
